\documentclass[letterpaper,11pt]{article}

% ---------- Encoding & Fonts ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{lmodern}
\usepackage{bold-extra}

% ---------- Unicode safety ----------
\usepackage{newunicodechar}

% Fix Unicode characters from copy/paste
\DeclareUnicodeCharacter{00A0}{ } % NBSP → normal space
\DeclareUnicodeCharacter{2013}{--} % en dash
\DeclareUnicodeCharacter{2014}{---} % em dash

% ---------- Layout & Style ----------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{bookmark} % fixes hyperref rerun warning
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome}
\input{glyphtounicode}

\pdfgentounicode=1

% ---------- Page Style ----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\footskip}{5pt} % fixes fancyhdr warning

% ---------- Margins ----------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---------- Section Formatting ----------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% ---------- Custom Commands ----------
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
  \item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4}
  \end{tabular*}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeRole}[2]{
  \item[]
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small#2}
  \end{tabular*}
}

\begin{document}

%---------- HEADING ----------
\begin{center}
  {\Huge \scshape Marco Martinelli} \\ \vspace{3pt}
  \small
  \faAt\ \href{mailto:smartinellimarco@icloud.com}{smartinellimarco@icloud.com} $|$
  \faGithub\ \href{https://github.com/smartinellimarco}{GitHub}
\end{center}

%----------- EXPERIENCE -----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{\href{https://www.splight.com/}{Splight}}{Argentina}
{Senior Software Engineer}{Jan 2023 -- Present}
\resumeItemListStart
  \resumeItem{Deployed Prefect to orchestrate data processing pipelines and machine learning workflows.}
  \resumeItem{Engineered synchronous and event-driven services using containerized and serverless architectures, managing communication, networking, and data storage. \\
  \textbf{Stack:} \footnotesize{Python, Go, gRPC, IoT Core, Kafka, Kinesis, SQS, EKS, Lambda, PostgreSQL, DynamoDB, MongoDB, Redis, QuestDB, S3.} \\
  \textbf{Concepts:} \footnotesize{Clean Architecture, SOLID, Concurrency (Asyncio, Goroutines), Parallelism (Multithreading).}}
  \resumeItem{Implemented platform-wide observability, including log aggregation, distributed tracing, and real-time alerting. \\
  \textbf{Stack:} \footnotesize{Datadog, Prometheus, OpenSearch}}
  \resumeItem{Developed and released Python libraries, CLI tools, GitHub Actions, and Terraform/Pulumi providers to support Infrastructure as Code (IaC) and streamline automated deployments across the platform.}
\resumeItemListEnd

\resumeSubheading
{\href{https://winclap.com/}{Winclap}}{Argentina}
{Lead Data Scientist}{Sep 2022 -- Jan 2023}
\resumeItemListStart
  \resumeItem{Led the development of a data-driven platform leveraging airflow and machine learning models to optimize marketing budget allocation and maximize ROI.}
  \resumeItem{Defined team objectives, roadmap planning, and execution oversight.}
  \resumeItem{Led hiring processes, technical interviews, and provided mentorship and career guidance.}
  \resumeItem{Maintained regular communication with stakeholders on project progress and outcomes.}
\resumeItemListEnd

\resumeSubheading
{\href{https://www.mercadolibre.com/}{Mercado Libre}}{Argentina}
{Senior Machine Learning Engineer}{Jul 2022 -- Sep 2022}
\resumeItemListStart
  \resumeItem{Researched, benchmarked, and developed Python libraries for text and image embedding techniques, adopted by multiple teams and minimizing feature rework across company-wide initiatives.}
  \resumeItem{Served as a mentor in internal machine learning training programs.}
  \resumeItem{Led technical interviews, roadmap planning, and team onboarding.}
\resumeItemListEnd

\resumeRole{Semi Senior Machine Learning Engineer}{Mar 2021 -- Jul 2022}
\resumeItemListStart
  \resumeItem{Developed computer vision pipelines for fraud prevention and identity verification, applying OCR, object detection, and classification models to credit card and identity document scans.}
  \resumeItem{Applied object detection to identify brand logos, enabling downstream models to detect counterfeit clothing and improving detection rates by 20\%.}
\resumeItemListEnd

\resumeRole{Junior Machine Learning Engineer}{Mar 2020 -- Mar 2021}
\resumeItemListStart
  \resumeItem{Built computer vision systems for warehouse automation, including barcode and license plate recognition, and detection of mispositioned packages on conveyor belt sorters.}
  \resumeItem{Implemented face matching and liveness detection pipelines for KYC processes.}
\resumeItemListEnd

\resumeRole{Software Developer Intern}{Jun 2019 -- Mar 2020}
\resumeItemListStart
  \resumeItem{Trained image classification and detection models to enforce marketplace quality standards and detect non-compliant listings.}
  \resumeItem{Optimized ML model inference using ONNX, TensorRT, quantization, pruning, and mixed-precision techniques, including a high-impact initiative (400k images/minute) that reduced costs by 10$\times$ making its deployment affordable.}
  \resumeItem{Developed semantic segmentation models to extract clothing from user images, enabling visual search in the marketplace.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- EDUCATION -----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{Universidad Nacional de Córdoba}{Argentina}
{M.Sc. in Computer Science}{Mar 2019 -- Present}

\resumeSubheading
{Universidad Nacional de Córdoba}{Argentina}
{B.Sc. in Computer Science}{Mar 2015 -- Mar 2019}

\resumeSubHeadingListEnd

%----------- CERTIFICATIONS -----------
\section{Certifications}
\resumeSubHeadingListStart
\item \small{
\textbf{First Certificate in English (B2)} — Cambridge Language School \\
Credential ID: 13BAR6121018 \hfill Dec 2013
}
\resumeSubHeadingListEnd

\end{document}
